--- 
title: "Marvin's First Book"
author: "Marvin (Cheng) Min"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is Marvin's first online book"
---

# How to make Kung Pao Chicken

Spicy chicken with peanuts, similar to what is served in Chinese restaurants. It is easy to make, and you can be as sloppy with the measurements as you want. They reduce to a nice, thick sauce. Substitute cashews for peanuts, or bamboo shoots for the water chestnuts. You can't go wrong! Enjoy!



## Ingredients

* 1 pound skinless, boneless chicken breast halves - cut into chunks
 
* 2 tablespoons white wine
 
* 2 tablespoons soy sauce
 
* 2 tablespoons sesame oil, divided
 
* 2 tablespoons cornstarch, dissolved in 2 tablespoons water
 
* 1 ounce hot chile paste
 
* 1 teaspoon distilled white vinegar
 
* 2 teaspoons brown sugar
 
* 4 green onions, chopped
 
* 1 tablespoon chopped garlic
 
* 1 (8 ounce) can water chestnuts
 
* 4 ounces chopped peanuts

## Directions

### Step 1
To Make Marinade: Combine 1 tablespoon wine, 1 tablespoon soy sauce, 1 tablespoon oil and 1 tablespoon cornstarch/water mixture and mix together. Place chicken pieces in a glass dish or bowl and add marinade. Toss to coat. Cover dish and place in refrigerator for about 30 minutes.

### Step 2
To Make Sauce: In a small bowl combine 1 tablespoon wine, 1 tablespoon soy sauce, 1 tablespoon oil, 1 tablespoon cornstarch/water mixture, chili paste, vinegar and sugar. Mix together and add green onion, garlic, water chestnuts and peanuts. In a medium skillet, heat sauce slowly until aromatic.

### Step 3
Meanwhile, remove chicken from marinade and saute in a large skillet until meat is white and juices run clear. When sauce is aromatic, add sauteed chicken to it and let simmer together until sauce thickens.


# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
